(1) Maybe user should have a option to check those false sharing inside stack variables.
(2) Should we use a thread index instead to save some spaces? Also, maybe it is better for the performance. 
    Generally, we will not have two threads that are accessing the same subheap. However, we may have to use
    the pthread\_t for comparison since it is unique? but actually it is not.
    We should use the unique heap in order to avoid the lock usage and overlapping (Diehard problem). In Diehard,
    two threads can use the same heap every time. 
    Also, we may introduce the current pointer in the thread library so that we can know corresponding information quickly. 
    whenever all children threads has been exited, then we should possibly update the 
    So we should use a

(3) Should we have an internal heap which also use tid to index their subheap.
(4) When there are multiple files there, how we can instrument every file one by one? Design a makefile to do this automatically. 

(a) Inserting the into clang so that we do not need to change the make file for each files.
(b) We will keep track of each read/write accesses instead of only checking once for each basic block.


Improving the performance step by step
(1) Avoiding using the singleton if we can use the simple variable.
(2) Trying to use the sampling (100 instructions we only sample one).

(4) How to sample those accesses. We donot want to loose those cache invalidations. 
So for each cache line, we are using the cache line based sampling mechanism. 
In the non-sampling phase, we will not update everything. 

However, there is a per-thread based sampling. For example, we only sample those accesses in the 
first 500 over 1000 accesses. However, we may lost a lot of interleaving accesses by doing this. 

If we are using the system level accessCount, for example, updating this shared accesses can cause a lot of
invalidations - which cause a lot of performance problem by using the shared account.

Also, we should try to implement those very basic accesses incremental in the first level instead of inside a very deep level.


