% Make sure to put back 

\date{} % \vspace*{-0.2in}}

\documentclass{sigplanconf}
\usepackage{endnotes,xspace}
\nocaptionrule

\newcommand{\footnotenonumber}[1]{{\def\thempfn{}\footnotetext{\small #1}}}
\usepackage[normalem]{ulem}
\usepackage{graphicx}

\usepackage{mathptmx} % rm & math
\usepackage[scaled=0.90]{helvet} % ss
\usepackage{courier} % tt
\normalfont
\usepackage[T1]{fontenc}

% \usepackage{lmodern}
% \usepackage{times}
\usepackage{subfigure}
\usepackage{url}
\urlstyle{rm}
\usepackage[
      colorlinks=false,    %no frame around URL
      urlcolor=black,    %no colors
      menucolor=black,    %no colors
      linkcolor=black,    %no colors
      pagecolor=black,    %no colors
]{hyperref}

\usepackage{color}
\usepackage{listings}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{comment} 
\usepackage{setspace}
\singlespacing
%\onehalfspacing
\newtheorem{thm}{Theorem}
\newtheorem{prop}[thm]{Proposition}
\newtheorem{cor}[thm]{Corollary}
\newtheorem{lem}[thm]{Lemma}
\newtheorem{defn}[thm]{Definition}

\newcommand{\dthreads}{\textsc{Dthreads}}
\newcommand{\Dthreads}{\textsc{Dthreads}}
\newcommand{\pthreads}{\texttt{pthreads}}

\newcommand{\cfunction}[1]{{\bf \tt #1}}
\newcommand{\malloc}{\cfunction{malloc}}
\newcommand{\realloc}{\cfunction{realloc}}
\newcommand{\free}{\cfunction{free}}
\newcommand{\madvise}{\cfunction{madvise}}
\newcommand{\brk}{\cfunction{brk}}
\newcommand{\sbrk}{\cfunction{sbrk}}
\newcommand{\mmap}{\cfunction{mmap}}
\newcommand{\munmap}{\cfunction{munmap}}
\newcommand{\mprotect}{\cfunction{mprotect}}
\newcommand{\mlock}{\cfunction{mlock}}

\hyphenation{app-li-ca-tion}
\hyphenation{Die-Hard}
\hyphenation{Ar-chi-pe-la-go}
\hyphenation{buf-fer}

\lstset{language=c++, basicstyle=\ttfamily\scriptsize,frame=trbl,tabsize=4,numbers=left,numberstyle=\tiny}

\definecolor{Gray}{cmyk}{0,0,0,0.5}

\begin{document}

\conferenceinfo{PLDI 2011,} {June 4--8, San Jos\'e, California, USA.}
\CopyrightYear{2011}
\copyrightdata{XXX-X-XXXXX-XXX-X/XX/XX}

\title{\textsc{Dthreads}: Efficient and Deterministic Multithreading}

\authorinfo{\emph{authorship list removed for anonymity}}

%\authorinfo{
%Tongping~Liu \and Charlie~Curtsinger \and Emery~D.~Berger}
%{Dept.\ of Computer Science \\ University of Massachusetts, Amherst \\
%Amherst, MA 01003} {\{tonyliu,charlie,emery\}@cs.umass.edu}

\maketitle

\begin{comment}
\end{comment}

\begin{abstract}
Multithreaded programming is notoriously difficult to get right.  A
key problem is non-determinism, which complicates debugging, testing,
and reproducing errors in multithreaded applications. One way to
simplify multithreaded programming is to enforce deterministic
execution. However, past deterministic systems are incomplete
or impractical. Language-based approaches require programmers to write
their code in specialized languages. Other systems require program
modification, do not ensure determinism in the presence of data
races, do not work with general-purpose multithreaded programs, or
suffer substantial performance penalties (up to $8\times$ slower
than \pthreads{}) that limit their usefulness.

This paper presents \dthreads{}, an efficient deterministic
multithreading system for unmodified C/C++ applications. \Dthreads{}
not only prevents semantic errors like race conditions and deadlocks,
but also can enhance performance by eliminating false sharing of cache
lines. \dthreads{} combines per-thread memory isolation and a
deterministic commit protocol to ensure robust deterministic execution
with low runtime overhead. Experimental results show that \dthreads{}
substantially outperforms a state-of-the-art deterministic runtime
system, and often matches---and occasionally exceeds---the performance
of \pthreads{}.
\end{abstract}

\category{D.1.3}{Programming Techniques}{Concurrent Programming--Parallel Programming}
\category{D.2.5}{Software Engineering}{Testing and Debugging--Debugging Aids}

\terms
Design, Reliability, Performance

\keywords
Deterministic Multithreading, Determinism, Parallel Programming, Concurrency, Debugging,
Multicore


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Introduction}
\input{introduction}

\section{\Dthreads{} Architecture}
\input{dthreads-architecture}

\section{Discussion}
\input{discussion}

\section{Evaluation}
\input{evaluation}

\section{Related Work}
\input{related-work}

\section{Future Work}
\input{future-work}
% eliminate global lock
% possibly adopting a page-ownership protocol as used by ...

\section{Conclusion}
\input{conclusion}

{
\bibliographystyle{abbrv}
\bibliography{dthreads,emery}
}

\end{document}
